%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original author:
% Rahul Chauhan (http://rahulchauhan.net)
%
% Original repository:
% https://github.com/rahulworld/rahulworld-Resume
%
% Modified By:
% Nikhil Rajesh (https://nikhilrajesh.com)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{resume}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=5mm,
 top=5mm,
 }

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Nikhil Rajesh}\\
\end{large}
Final Year (B.Tech)\\
Computer Science $\&$  Engineering\\ 
at NIT Calicut \\ 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
\noindent\rule{5cm}{0.8pt}

\href{https://github.com/ph4t3}{Github:// \custombold{ph4t3}} \\
\href{https://www.linkedin.com/in/nikhil-rajesh1999}{LinkedIn://  \custombold{nikhil-rajesh1999}}
\vspace{6pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.8pt}
\subsection{OS}
GNU/Linux, Windows
\vspace{6pt}
\subsection{Languages}
C/C++, Python, Go, Lua, \\
Javascript/Typescript
\vspace{6pt}
\subsection{Framework}
NodeJs, NestJs, Angular
\vspace{6pt}
\subsection{Databases}
MySQL, PostgreSQL, MongoDB
\vspace{6pt}
\subsection{Others}
Markdown, Git, Vim
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{5cm}{0.8pt}

Data Structures\\
Algorithms\\
Discrete Mathematics\\
Operating Systems\\
DBMS\\
Computer Organization\\
Compiler Design\\
Computer Networks
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.8pt}\\
\datecolor{2018-Present}
\subsection{B.Tech. in CSE}
NIT Calicut \\
CGPA : 8.97/10\\
\vspace{8pt}
\datecolor{2015-2017}
\subsection{Senior Secondary}
Devamatha CMI PS, Thrissur\\
Percentage: 95.4\%\\
\vspace{8pt}

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
\vspace{10pt}
\hspace*{0pt}\hfill Vadakkekalathil House, Kadavallur \\
\hspace*{0pt}\hfill Thrissur, Kerala, 680543, India \\
\hspace*{0pt}\hfill +91-9061460018 \\
\hspace*{0pt}\hfill \textbf{\href{mailto:mail@nikhilrajesh.com}{mail@nikhilrajesh.com}} \\
\hspace*{0pt}\hfill \textbf{\href{http://nikhilrajesh.com}{nikhilrajesh.com}} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{9.4pt}
\section{Experience}
\noindent\rule{12.5cm}{0.8pt}
\subsection{\href{https://cisco.com}{\custombold{Cisco}}}
\noindent Technical Undergraduate Intern \hfill \emph{May, 2021 - Present}
\vspace{1mm}
\begin{tightemize}
    \item Developed a web GUI based Bandwidth Calculator for the emerging 5G equipments
    \item Quickly learned new skills and applied them to daily tasks, improving efficiency
and productivity.
\end{tightemize}
\sectionsep

\subsection{\custombold{\href{https://athena.nitc.ac.in/}{Software Systems Lab NITC}}}
\noindent System Administrator \hfill \emph{Apr, 2021 - Present}
\vspace{1mm}
\begin{tightemize}
    \item In charge of maintaining 75 lab systems and more than 9 servers.
\end{tightemize}
\sectionsep

\subsection{\custombold{\href{http://ieee.nitc.ac.in/}{IEEE Computer Society NITC}}}
\noindent Secretary \hfill \emph{Feb, 2020 - Jan, 2021}
\vspace{1mm}
\begin{tightemize}
    \item Implemented various web based applications that enhances the features of their B2B e-commerce platform.
    \item Collaborated effectively with members of software development team and personnel in other departments.
\end{tightemize}
\sectionsep

\subsection{\custombold{\href{https://storilabs.com/}{Storilabs System Technologies}}}
\noindent Software Intern \hfill \emph{Sep, 2019 - Sep, 2020}
\vspace{1mm}
\begin{tightemize}
    \item Implemented various web based applications that enhances the features of their B2B e-commerce platform.
    \item Collaborated effectively with members of software development team and personnel in other departments.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\noindent\rule{12.5cm}{0.8pt}

\subsection{\href{https://exposnitc.github.io/}{\custombold{eXpOS}} \hfill \href{https://git.io/JnA77}{git.io/JnA77}}
\vspace{1mm}
Build a toy operating system as part of the Operating Systems Lab course from NIT Calicut. Learned the implementation of various OS data structures and kernel routines during the course of the project.
\sectionsep

\subsection{\href{https://silcnitc.github.io/}{\custombold{ExpL}} \hfill \href{https://git.io/JnAdH}{git.io/JnAdH}}
\vspace{1mm}
Build a toy compiler as part of the Compiler Lab course from NIT Calicut. Learned the functioning of a compiler for a simple object oriented language. The compiler was build using LEX, YACC \& C.
\sectionsep

\subsection{\href{https://infinitum.clubmathematica.com/}{\custombold{Infinitum}}}
\vspace{1mm}
Infinitum is an annual inter school quizzing event conducted by Club Mathematica, NIT Calicut. Due to the pandemic it was conducted as an online event in 2021. I worked as a full stack developer in the Infinitum team to build a backend in NestJs as well as an admin panel using Angular.
\sectionsep

\subsection{\href{http://tathva.org/}{\custombold{ZerothAttempt MockJEE, Tathva 2020}}}
\vspace{1mm}
Zeroth Attempt is a Online Mock JEE examination conducted as a part of Tathva 2020 to raise funds against the prevailing pandemic, COVID'19. I worked as a software developer in the Zeroth Attempt team to create a backend to facilitate the smooth conduct of the exam. The project was done using NodeJS.
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}